Contextual Identity: Towards Usable Privacy

### 2013-02-28 paper.tex
label, label

\section{Research directions}
We propose new research directions based on the following questions.
\begin{itemize}
\item How do users think about identity?
\item What can we infer about identity?
\item What threat models (audiences, topics) are important to users?
\item What are users already doing to preserve contextual identities?
\end{itemize}

@@

Although a user may subconsciously be aware of their contextual identities,
expecting users to enumerate their identities and manually curate them is
probably too burdensome. Firefox has a Profile Manager, but it is so difficult
to use that it will be removed.\footnote{See
\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Tang et
al.~show that most people do not take the time to create labels and maintain
friend lists~\cite{tang}. However, the same authors show how to use
heterogeneous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

Further research is required to determine what constitutes a contextual
identity. The contextual integrity model from Barth et al.~does not capture
these notions adequately.

(This is weak)
If users' contextual identities are primarily task oriented, it may be
possible to infer tasks from the user's activity. For example, the
\texttt{about:profile} Firefox extension uses the Open Directory Project and
Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.

\subsection{Automatic mitigations for information leakage}
One can categorize a user's contextual identities and prevent information
leakage between them.  For example, preventing third-party cookies from being
read and set across task boundaries means that targeted ads for dating would
not follow the user when visiting a technology news site. Knowing the user's
current contextual identity also allows the browser to suppress URL bar
suggestions that aren't relevant to that identity, protecting the user from
both shoulder-surfing and distraction.

Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
for private browsing mode, and thus interaction with extensions, treatment of
cookies, history, and bookmarks upon entering and exiting this mode are
different and serve different use cases. Depending on user desire, the threat
model for using private browsing mode may be other household members, or it may
be a service to which the user wants to limit cookie leakage.

Another partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}.
Because we can categorize the type of service by URL
as \texttt{about:profile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.

>>>>

\section{Research directions}
We propose new research directions based on the following questions.
\begin{itemize}
\item How do users think about identity?
\item How do users manage identity?
\item How can we improve tools for managing identity?
\end{itemize}

@@

\subsection{How do users manage identity?}
\paragraph{Profile management}
Although a user may subconsciously be aware of their contextual identities,
expecting users to enumerate their identities and manually curate them is
probably too burdensome. Firefox has a Profile Manager, but it is so difficult
to use that it will be removed.\footnote{See
\url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}.} Tang et
al.~show that most people do not take the time to create labels and maintain
friend lists~\cite{tang}. However, the same authors show how to use
heterogeneous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

\paragraph{Private browsing mode}
Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
for private browsing mode, and thus interaction with extensions, treatment of
cookies, history, and bookmarks upon entering and exiting this mode are
different and serve different use cases. Depending on user desire, the threat
model for using private browsing mode may be other household members, or it may
be a service to which the user wants to limit cookie leakage.

\subsection{How can we improve identity management tools?}
If users' contextual identities are primarily task-oriented, it may be
possible to infer tasks from the user's activity. For example, the
\texttt{about:profile} Firefox extension uses the Open Directory Project and
Alexa to categorize URLs that the user has visited~\cite{aboutprofile}.

\paragraph{Mitigating information leaks}
Given a user's contextual identities, we may be able to prevent information
leakage between them.  For example, preventing third-party cookies from being
read and set across task boundaries means that targeted ads for dating would
not follow the user when visiting a technology news site. Knowing the user's
current contextual identity also allows the browser to suppress URL bar
suggestions that aren't relevant to that identity, protecting the user from
both shoulder-surfing and distraction.

\paragraph{Mitigating unwanted linkage}
Another partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}.
Because we can categorize the type of service by URL
as \texttt{about:profile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.
